R Notebook

### 2022-08-30 hw1-1/abhinav/knn.Rmd
residual commits
KNN code updated

---
title: "R Notebook"
output: github_document
---

@@

```{r}
# need to iterate for lower values of K
plot(pred_table)
```

```{r}
knn_pred<-vector(mode="list",length = dim(knn_data)[1])
pred_table<-data.frame(k_val=numeric(0),acc_val=double(0))
for (k0 in seq(1,25,by=3)){
  for (i in 1:nrow(knn_data)){
    knn_model_v0<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="optimal",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==knn_data$R1[i]) 
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(knn_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
```

>>>>

---
title: "R Notebook"
output: html_document
---

@@

```{r}
# iteration over all values of K in increments of 10 to get a probable range where max accuarcy is attained
plot(pred_table)
```

```{r}
# Rectangular(unweighted) kernel as optimised 
knn_pred<-vector(mode="list",length = dim(knn_data)[1])
pred_table<-data.frame(k_val=numeric(0),acc_val=double(0))
for (k0 in seq(1,nrow(knn_data),by=10)){
  for (i in 1:nrow(knn_data)){
    knn_model_v0<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==knn_data$R1[i]) 
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(knn_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
plot(pred_table)
```

```{r}
knn_pred<-vector(mode="list",length = dim(knn_data)[1])
pred_table<-data.frame(k_val=numeric(0),acc_val=double(0))
for (k0 in seq(1,30,by=1)){
  for (i in 1:nrow(knn_data)){
    knn_model_v0<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.integer(round(fitted(knn_model_v0),digits = 0)==knn_data$R1[i]) 
  }
  percent_accuracy<-round(as.double(sum(unlist(knn_pred)))/nrow(knn_data),digits =2)
  pred_table[nrow(pred_table)+1,]=c(k0,percent_accuracy)
}
# Iteration over lower values of K
plot(pred_table)
```

```{r}
#set of all k values where overall accuracy is maximum
pred_table$k_val[pred_table$acc_val==max(pred_table$acc_val,na.rm=TRUE)]
```

```{r}
#anshit to review from here -> loop over k and get a dataframe with k,threshold and auc value, accuracies
k0=21
test_pred<-data.frame(pred_val=double(0),act_class=numeric(0))
for (i in 1:nrow(knn_data)){
    knn_model_v1<-kknn(R1~.,train = knn_data[-i,],test = knn_data[i,],k=k0,kernel="rectangular",scale = TRUE)
    knn_pred[i]<-as.double(fitted(knn_model_v1))
    test_pred[nrow(test_pred)+1,]=c(knn_pred[i],knn_data$R1[i])
}
```

```{r}
accuracy_knn <- function(df){
  acc_overall = sum(df$act_class == df$pred_class)/nrow(df)
  df_1 = df[df$act_class > 0,]
  df_0 = df[df$act_class == 0,]
  acc_1 = sum(df_1$act_class == df_1$pred_class)/nrow(df_1)
  acc_0 = sum(df_0$act_class == df_0$pred_class)/nrow(df_0)
  return (c(acc_overall, acc_1, acc_0))
}
```

```{r}
threshold_auc<-data.frame(threshold_val=double(0),auc_val=double(0),acc_overall=double(0),acc_1=double(0),acc_0=double(0))
for(t0 in seq(0.2,0.8,by=0.02)){
  f0<-function(x,t=t0){
    ifelse(x>t,1,0)
  }
  test_pred$pred_class<-apply(data.frame(test_pred$pred_val),1,f0)
  # function to get overall , 0's and 1's accuracy
  # accuracy_knn(test_pred)
  auc_val<-auc(test_pred$act_class,test_pred$pred_class)
  threshold_auc[nrow(threshold_auc)+1,]=c(t0,auc_val,accuracy_knn(test_pred))
}
```

```{r}
head(threshold_auc)
accuracy_knn(test_pred)
```

```{r}
#roc_score=roc(test_pred$act_class,test_pred$pred_class)
#plot(roc_score ,main ="ROC curve --KNN ")
print(paste("Max AUC score :" ,round(max(threshold_auc$auc_val),2)))
print(paste("Threshold values for which max AUC score is attained", threshold_auc$threshold_val[threshold_auc$auc_val==max(threshold_auc$auc_val,na.rm=TRUE)]))
```
